MSB1015_Assignment 2

### 2019-10-13 MSB1015_Assignment2_SuzannetenHage.Rmd
Improved code section 4 + Note on section 3
* Section 4: Fixed an error that occurred because an old name was used. 
* Section 4: Added a print statement, so the code automatically prints the error of the null model. 
* Section 3: Added a note that the errors of both the null model and PLS model are dependent on the random splitting of the data into training and test set.

**4. Null model**
The null model is the most simple model possible: the mean of the data. This model can be used as a reference to see whether the PLS model performs better.

@@

#Create null_model
null_model <- mean(train$data_raw.bp)

#Get error of null model
error_null_model <- rmse(test$data_raw.bp, null_model)

>>>>

Note: The error of both the null and PLS models is dependent on the random splitting in training and test set. If you run the code, it is expected that the error differs from the error reported here.

**4. Null model**
The null model is the most simple model possible; the mean of the data. This model can be used as a reference to see whether the PLS model performs better.

@@

#Create null_model
null_model <- mean(train$data_wikidata.bp)

#Get error of null model
error_null_model <- rmse(test$data_wikidata.bp, null_model)

#Print the error
print(paste0("The error of the Null model is ", error_null_model))

#error: 250.68 degrees Kelvin.
